Manuscript draft

### 2019-09-12 manuscript/Discussion_KAT.Rmd
Update Discussion_KAT.Rmd

**[needs strong concluding paragraph]**
[Our analysis holds some important implications for our understanding of how forest carbon cycling relates to climate and, by extension, how it is likely to respond to climatic warming. We see no evidence that there are major differences in how the various components of forest autotrophic carbon cycling relate to climate or, by extension, any distinct trends in C allocation across the global scale (Fig. 3). ]

### Acknowledgements
Scholarly Studies
ForestGEO
DOE database

>>>>

Our analysis clarifies the big picture of how FACF varies with latitude and climate on a global scale, with some important implications for how forest carbon cycling relates to climate and, by extension, how it is likely to respond to climatic warming. Contrary to some previous suggestions, we find no support for non-linear trends in mature forest C cycling with respect to latitude or $MAT$, and no distinct trends in C allocation across the global scale (Fig. 3). The implication is that under warmer conditions with similar moisture availability--and within the temperature range to which forest communities are adapated and acclimatized--higher temperatures result in a generalized acceleration of FACF, with no major shifts in C allocation among subsidiary fluxes. Of course, actual climatic changes will result in very different sets of conditions than represented across geographic gradients in climate, but our analysis clarifies the big picture as to how carbon cycles through forest ecosystems that have developed under relatively stable climatic conditions. As we enter a period of accelerating climatic change, understanding of the fundamental climatic controls on FACF sets a foundation for understanding patterns of change. **[work on this]**

### Acknowledgements
Scholarly Studies
ForestGEO
Compilatin of the ForC database was originally funded by DOE
